Discovering causal factors with back-to-back regression

### 2019-05-22 paper/meg_exps.tex
add paragraph meg stabilization

Finally, back-to-back regression was fit as decribed earlier using two additional stability tricks designed to minimize the impact of bagging.
First the $G$ ridge regression was broken-down with SVD blablabla
Second, $X$ was regularized using a maximal likelihood blablabla
Third, no regularization

Back-to-back regression directly leads to $\hat E$.

>>>>

Finally, we adapted back-to-back regression with two changes. First, to avoid getting a slightly positively-biased estimate of the factors contributing to the MEG signal, we swap the Tikhonov regularization of the first regression $G$ with a trunkated regularization. Trunkation was fitted by maximum likelihood estimate, as implemented in scikit-learn principal component analysis. Second, to minimize the variance increase induced by bagging, we computed the inverse regularized covariance matrices outside bagging:
\begin{equation}
G = (Y_^T Y+\lambda_Y I)^{-1} Y_i^T X_i
\end{equation}

\begin{equation}
\hat X_j = Y_j \cdot G^T
\end{equation}
where i and j are partition of the data.
